Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-01 docs/00-manuscripts/ieee/ieee-manuscript.tex
clarify that meng2018 used FS
add interpreation of ale plots

In this work we applied permutation-based feature importance and \ac{ALE} plots to calculate feature importance for the HR dataset.
With the limitations of both methods in mind we aimed to get a general overview of the feature importance of the hyperspectral bands while trying to avoid the over-interpretation of results.
We used the best-performing algorithm from the HR task (i.e. SVM) to calculate the feature importance.
ALE plots were not discussed in greater detail and are available as supplementary material.

@@

\noindent The decision to use a buffer of two meters for the extraction of an observation's reflectance value was a complex decision.
Due to the reported geometric offset of up to 1 m within the hyperspectral data, the possibility of assigning a value to an observation which would actually refer to a different observation was reasonably high.
By using a buffer of two meters (or more), the probability of including information from other trees into the final value increases, blurring the actual value of the tree observation.
However, the difference between single pixel values might often be higher than the difference between a smoothed value composed out of a buffer.
In our view using a buffer of two meters was a good compromise between including information of too many surrounding trees and not accounting for the geometric offset at all.
Even though no results showing the influence of multiple buffer values on the extraction were provided, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

@@

This area has the highest ability to distinguish between reflectances related to a high density / high healthiness of vegetation and their respective opposites \cite{horler1983}.
It is also worth mentioning that four out of ten of the most important features of dataset HR lie between 920 nm and 1000 nm.
Looking at the spectral curves of the plots, we can observe quite some dynamic in this area, especially for Oiartzun, which might explain why these features were considered as important by the model.

@@

@@

Studies focusing on tree-level defoliation used ground-level methods such as \ac{ALS} or \ac{LiDAR}\cite{meng2018, kalin2019}.
\cite{meng2018} used \ac{OLS} regression methods while \cite{kalin2019} retrieved information from ground-level RGB photos using \ac{CNN}.
However, both did not use spatial \ac{CV} or \ac{FS}.
\cite{goodbody2018} used a \ac{PLS} model with high-resolution \ac{DAP} to predict cumulative defoliation caused by the spruce budworm.
Study results indicated that spectral metrics were found to be most helpful for the model.
Incorporating such metrics (both spectral and structural) could be a possible enhancement for future works.

@@

\section{SVM ALE plots for task VI}

@@

\section{Correlation among filter methods}

>>>>

In this work we applied permutation-based feature importance and \ac{ALE} plots to calculate feature importance for the HR dataset, with a focus on the former.
With the limitations of both methods in mind we aimed to get a general overview of the feature importance of the hyperspectral bands while trying to avoid the over-interpretation of results.
We used the best-performing algorithm from the HR task (i.e. SVM) to calculate the feature importance.
The ALE plots show a small relative change compared to their respective mean effects for all chosen features ($< \mid 0.001 \mid$) (\autoref{fig:fi-hr-ale}).
Most ALE curves show a high dynamic across the value range of each variable, within their respective effect range.

@@

The decision to use a buffer of two meters for the extraction of an observation's reflectance value was a complex decision.
Due to the reported geometric offset of up to 1 m within the hyperspectral data, the possibility of assigning a value to an observation which would actually refer to a different observation was reasonably high.
By using a buffer of two meters (or more), the probability of including information from other trees into the final value increases, blurring the actual value of the tree observation.
However, the difference between single pixel values might often be higher than the difference between a smoothed value composed out of a buffer.
In our view using a buffer of two meters was a good compromise between including information of too many surrounding trees and not accounting for the geometric offset at all.
Even though no results showing the influence of multiple buffer values on the extraction were provided, we hypothesize that the relationships between features would not change substantially, leading to the almost identical model results.

@@

This area has the highest ability to distinguish between reflectances related to a high density / high healthiness of vegetation and their respective opposites \cite{horler1983}.
It is also worth mentioning that four out of ten of the most important features of dataset HR lie between 920 nm and 1000 nm.
Looking at the spectral curves of the plots, one can observe some apparent reflectance differences in this area, especially for Oiartzun, which might explain why these features were considered as important by the model.

@@

% ALE plots
The ALE plots are hard to interpret due to their semi-meaningful absolute values which differ for each band.
For example, a reflectance value of 100 has a very different meaning in B67 than in B124 because for the latter reflectance values of vegetation are naturally higher.
Hence, a reflectance value of 100 would be considered high for B67 but low for B124 with respect to a spectral curve of vegetation.
However, no baseline reflectance value for every feature exists since the absolute reflectance values depend on the sensor characteristics.
Hence, it is hard to make reasonable interpretations of harsh drops/jumps within curves of certain features, e.g. the one at value 240 for feature B115.
ALE plots can be a powerful tool for interpreting feature importances of correlated features but might be limited in interpretability if the absolute feature values are only semi-meaningful.

@@

Studies focusing on tree-level defoliation used ground-level methods such as \ac{ALS} or \ac{LiDAR}\cite{meng2018, kalin2019}.
\cite{meng2018} used \ac{OLS} regression methods while \cite{kalin2019} retrieved information from ground-level RGB photos using \ac{CNN}.
However, both did not use spatial \ac{CV} and \cite{kalin2019} no \ac{FS}.
\cite{goodbody2018} used a \ac{PLS} model with high-resolution \ac{DAP} to predict cumulative defoliation caused by the spruce budworm.
Study results indicated that spectral metrics were found to be most helpful for the model.
Incorporating such metrics (both spectral and structural) could be a possible enhancement for future works.

@@

%\section{SVM ALE plots for task VI}

@@

\pagebreak
\section{Correlation among filter methods}
